State of the Practice for Lattice Boltzmann Method Software

### 2021-12-17 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
Update to LBM arXiv paper to use wider and shorter charts for the AHP results

We requested interviews from all 24 packages, with 4 positive responses.  To
send out interview requests we found we found contacts on the projects’ website,
or code repository, or publications, or the biographic pages of the teams’
institutions. We send at most two interview request emails to a contact for each
software package.  Meeting will typically be held using on-line meeting
software, like Zoom or Teams.  This facilitates recording and automatic
transcription of the meetings.

@@

\begin{figure}[h!]
	\begin{center}
		\includegraphics[width=1.0\textwidth]{./figures/installability_chart}
		\caption{AHP Installability Score}
		\label{Fig_Installability}
	\end{center}
\end{figure}

@@

The interview process
presented here was approved by the McMaster University Research Ethics Board
under the application number 
\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/MACREM/Application.pdf}
{MREB\#: 5219}.

This section presents the qualitative findings from data that was gathered
during interviews with developers for qualities listed in Section
~\ref{softwarequalities}. The interview questions are found in Appendix
~\ref{interviewquestions}.

Interviews with developers confirmed that these software packages are developed
by domain experts with backgrounds in physics, mathematics and mechanical
engineering. It was noted in these interviews that some of the developers do not
have formal software engineering education. Some of the development teams
include computer scientists. Despite a lack of visible domain documentation and
a resulting lower surface correctness and verifiability score, it is clear that
some of the software packages were developed by teams with significant domain
knowledge on account of the academic backgrounds of their developers.

Interviews suggested a more frequent use of both unit testing and continuous
integration in the development processes than what was observed from the initial
survey. For example, OpenLB, pyLBM, and TCLB use such methods during development
despite this not being explicitly clear from an analysis of the material
available online. The correctness and verifiability of such packages is not
measured well using surface analysis.

Several interviewed developers alluded to difficulty with testing the
correctness of large numbers of features, and some even manually tested program
output. The use of well defined unit testing tools could decrease the time spent
testing some feature.

@@

@@

>>>>

We requested interviews from all 24 packages, except Munubi, since Munubi was
added after our ethics approved study window had expired.  We were able to
recruit 4 developers to participate in our study.  To send out interview
requests we found we found contacts on the projects’ website, or code
repository, or publications, or the biographic pages of the teams’ institutions.
We send at most two interview request emails to a contact for each software
package.  Meeting will typically be held using on-line meeting software, like
Zoom or Teams.  This facilitates recording and automatic transcription of the
meetings.

@@

\begin{figure}[h!]
	\begin{center}
		\includegraphics[width=1.0\textwidth]{./figures/installability_chart.pdf}
		\caption{AHP Installability Score}
		\label{Fig_Installability}
	\end{center}
\end{figure}

@@

This section presents qualitative findings on software qualities as gleaned from
interviewing 4 developers. The full interview questions are found in
\citet{SmithEtAl2021}.

\subsection{Correctness and Verifiability}

Interviews with developers confirmed that these software packages are developed
by domain experts with backgrounds in physics, mathematics and mechanical
engineering. \wss{Could point to surveys that have shown the same thing.}  It
was noted in these interviews that some of the developers do not have formal
software engineering education. Some of the development teams include computer
scientists. Despite a lack of visible domain documentation and a resulting lower
surface correctness and verifiability score, it is clear that some of the
software packages were developed by teams with significant domain knowledge on
account of the academic backgrounds of their developers.

Interviews suggested a more frequent use of both unit testing and continuous
integration in the development processes than what was observed from the initial
survey. For example, OpenLB, pyLBM, and TCLB use such methods during development,
despite this not being explicitly clear from an analysis of the material
available online. \wss{Add this to threats to validity.}  The correctness and
verifiability of such packages is not measured well using surface analysis.

Several developers alluded to difficulty with testing the correctness of large
numbers of features, and some even manually tested program output. The use of
well defined unit testing tools could decrease the time spent testing some
feature.  \wss{link this to recommendations}

\subsection{Usability}

@@

\subsection{Understandability}

@@

- add a comparison to other studies
- add conclusions related to how LBM compares to other fields, and the "average" of all SC

- make recommendations in order of conservative to ``bleeding edge''
- add pointer to project checklists (as sent to Jacques, as promoted during workshop)

- value of tools to enforce good behaviour of developers, like R, like MOOSE infrastructure
